\documentclass[a4paper]{exam}

\usepackage{amsmath,amssymb, amsthm}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{titling}



% Header and footer.
\pagestyle{headandfoot}
\runningheadrule
\runningfootrule
\runningheader{CS/MATH 113, SPRING 2025}{Pset 02: Predicate Logic}{\theauthor}
\runningfooter{}{Page \thepage\ of \numpages}{}
\firstpageheader{}{}{}

% \printanswers %Uncomment this line

\title{Problem Set 02: Predicate Logic}
\author{Blingblong} % <=== replace with your student ID, e.g. xy012345
\date{CS/MATH 113 Discrete Mathematics\\Habib University\\Spring 2025}

% \qformat{\large\bf \thequestion.}
\boxedpoints

\begin{document}
\maketitle

\begin{questions}
    \question What is the difference between a predicate and a propositional?
    \begin{solution}
        % Enter solution here
    \end{solution}

    \question Let consider the following predicates:
    \begin{itemize}
        \item $P(x):$ $x$ an even number.
        \item $Q(x):$ $x$ is a prime number.
        \item $R(x,y):$ $x \geq y$.
        \item $S(x,y):$ $x$ is divisible by $y$.
        \item $T(x):$ $x$ is odd. 
    \end{itemize}
    The domain for quantifiers is the set of all natural numbers.
    Convert the following english statements in predicate logic.
    \begin{parts}
        \part There is a natural number that is even but not divisible by 3.
        \begin{solution}
            % Enter solution here
        \end{solution}

        \part All natural numbers are greater than 0 and if a natural number is divisible by 2 then it is even.
        \begin{solution}
            % Enter solution here
        \end{solution}

        \part There is a unique (only one) natural number that is even and prime.
        \begin{solution}
            % Enter solution here
        \end{solution}

        \part There is no natural number that is both even and odd. 
        \begin{solution}
            % Enter solution here
        \end{solution}

        \part All natural numbers that are either even or odd but not both if a natural number is even and greater than equal to 3 then if its prime then its not divisible by 2.
        \begin{solution}
            % Enter solution here
        \end{solution}
    \end{parts}
    


    \question Let consider the following predicates:
    \begin{itemize}
        \item $P(x):$ $x$ is a true Sigma.
        \item $Q(x):$ $x$ mews constantly.
        \item $R(x):$ $x$ is a skibidi rizzler.
        \item $S(x,y):$ $x$ will give $y$ knee surgery tomorrow.
        \item $T(x):$ $x$ works at the RO office. 
        \item $U(x):$ $x$ is a student in your class. 
        \item $V(x):$ $x$ will get A$^+$ in DM. 
    \end{itemize}
    The domain for quantifiers consists of everyone in UHU (Univerity of Habib University).
    Convert the following statements in English.
    \begin{parts}
        \part $\forall x T(x) \implies (P(x) \land Q(x) \land R(x))$
        \begin{solution}
            % Enter solution here
        \end{solution}

        \part $\exists x \exists y, T(x) \land U(y) \land (R(y) \lor S(x,y))$
        \begin{solution}
            % Enter solution here
        \end{solution}

        \part $\forall x  (U(x) \land (P(x)\lor R(x))) \implies V(x)$
        \begin{solution}
            % Enter solution here
        \end{solution}

        \part $\forall x \neg (\exists y \neg V(x) \land S(y,v))$
        \begin{solution}
            % Enter solution here
        \end{solution}

        \part $\forall x \exists y (V(x) \iff (T(y) \land U(x) \land S(x,y)) \lor \neg (\neg P(x) \lor \neg Q(x) \lor \neg S(x,y)))$
        \begin{solution}
            % Enter solution here
        \end{solution}
    \end{parts}

    \question Negate the following statements
    \begin{parts}
        \part $\exists y \forall x (P(y) \implies Q(x))$
        \begin{solution}
            % Enter solution here
        \end{solution}

        \part $\forall x \exists y ((P(x) \land \forall z Q(z)) \lor \neg P(y))$
        \begin{solution}
            % Enter solution here
        \end{solution}

        \part $\not\exists x \forall y \exists z (\neg P(x) \land Q(y)) \lor (P(x)\lor \neg R(y))$
        \begin{solution}
            % Enter solution here
        \end{solution}
    \end{parts}
    

      
\end{questions}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
